% options are:
% PhD, MSc (choose one)
% beforeExam (to make the personal thanks invisible)
\documentclass[MSc,beforeExam]{iitcsthesis}

\usepackage{times}
\usepackage{latexsym}
\usepackage{graphicx} % more modern
\usepackage{graphics}
\usepackage{subfigure}
\usepackage{natbib}

\usepackage{hyperref}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{latexsym}
\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{epstopdf}
\usepackage{url}
\usepackage{color}
\usepackage{wrapfig}
\usepackage{fancyvrb}
\usepackage{rotating}
\usepackage{enumerate}
\usepackage{tabulary}
\usepackage[table]{xcolor}

% the next 3 line is a fix in order to add the algorithmicx works with hebrew
\makeatletter
\def\@arabic#1{\number#1}
\makeatother

\usepackage{algpseudocode}
\usepackage{algorithmicx}
\usepackage[chapter]{algorithm}



% For some reason, the hebrew package clashes with the amsthm package. If you need a proof environment, you can uncomment the following:
%\usepackage{amssymb} %Needed for \blacksquare. Take care not to add this package twice...
%\newenvironment{proof}[1][Proof]{\par \textbf{#1.} }{\hspace{10pt}\hfill$\blacksquare$\par}
\begin{document}

\authorEnglish{Haim Cohen}

\titleEnglish{Multi-task Learning with a Shared Annotator}

\supervisorEnglish{The Research Thesis Was Done Under The Supervision
of Prof.~Koby Crammer in the Faculty of Electrical Engineering.}

\PublicationEnglish{\\Parts of this work were published in\\
``Learning Multiple Tasks in Parallel with a Shared Annotator''. 
\\Haim Cohen and Koby Crammer. NIPS 2014.}

\GregorianDateEnglish{December 2015}
\JewishDateEnglish{Tevet, 5776}  

\personalThanksEnglish{I would like to thank Koby for his remarkable guidance and support. \\
Thanks to my family for the support....}
%\financialThanksEnglish{The generous financial support of the Technion is gratefully acknowledged.}

\maketitleEnglish

% The English abstract should be 200-500 words long.
\abstractEnglish
We introduce a new multi-task framework, in which $K$ online
learners are sharing a single annotator with limited bandwidth. On
each round, each of the $K$ learners receives an input, and makes a
prediction about the label of that input. Then, a shared
(stochastic) mechanism decides which of the $K$ inputs will be
annotated. The learner that receives the feedback (label) may update
its prediction rule, and we proceed to the next round. We develop 
online algorithms for multi-task binary classification that learns in
this setting, and bound its performances in the worst-case
setting. The algorithms apply an exploration-exploitation approach in order to allocate the limited feedback in the way that reduces the total number of errors.  
Additionally, we show that our algorithm can be used to
solve two bandits problems: contextual bandits, and dueling bandits
with context, both allowed to decouple exploration and
exploitation. Empirical study with OCR data , vowel prediction (VJ
project) and NLP -sentiment analysis data shows that our algorithms outperforms algorithms that use
uniform allocation, and essentially makes more (accuracy) for the
same labour of the annotator.
\input{prela}

\chapter*{Abbreviations and Notations}
\begin{tabular}{lcl}
$SHAMPO$ & --- & SHared Annotator for Multiple PrOblems\\
$\Vert\vu \Vert$ & --- & $\ell_2$-norm of the vector $\vu$\\
$ECOC$ & --- & Error COrrecting Code\\
$OCR$ & --- & Optical Character Recognition\\
$NLP$ & --- & Natural language processing\\
$MFCC$ & --- & Mel-Frequency Cepstral Coefficients\\
\end{tabular}

%Or, if your tables are long, ``\usepackage{longtable}'' at the beginning, and then  ``\begin{longtable}[l]{lcl} ... \end{longtable}''

\allowdisplaybreaks[1]

\input{introduction}
\input{SharedAnnotatorSettings}
\input{SHAMPO}
\input{second_order}
\input{second_order_aggressive}
\input{multitask_to_multiclass}
\input{experiments}
\input{related_work}
\input{conclusions}

%\section*{Appendix}
%\addcontentsline{toc}{section}{Appendix}
%For some reason, you need to manually add stared sections to the the index file.

% Put the path to your bib file (or whatever else you use) here
\clearpage
%\bibliographystyle{fullname}
\bibliographystyle{plainnat}
\bibliography{bib}

% ********************** ADD THIS BACK ********************************
%\include{hebrewPart}
% *********************************************************************

% Actually, I found it much easier to have each chapter in a file of its own. Except for the Hebrew part, I put it all together in this example just to make things clear.

\end{document}
